Sparse Function-space Representation \\ of Neural Networks

### 2023-05-11 paper/main.tex
Abstratct

\begin{abstract}
% OLDER VERSION
%Sequential learning paradigms such as Continual Learning (CL) or Reinforcement Learning (RL) pose a challenge for gradient-based deep learning techniques as they struggle to incorporate new data and retain previous knowledge. Existing methods for converting neural networks from weight to function space allow a probabilistic treatment of the distribution over the function learned by the neural networks but are computationally expensive. We propose a method that converts a neural network to a low-rank functional representation as a sparse Gaussian process. With this approach, we can build a compact representation of the function encoded by the neural network that can replace previous data in continual settings and be used for fast adaptation in RL, avoiding full retraining of the model. 
%
% Rewrite on 2023-05-10
Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and fail to retain previous knowledge. We present a method that mitigates these issues by transforming a weight-space neural network to a low-rank function-space representation, via the so-called dual parameters. In contrast to previous work, we model the joint distribution across the entire data set rather than a subset. This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance. We demonstrate the proposed approach in quantifying uncertainty in supervised learning, maintaining a summary representation in continual learning, and in active learning.
\end{abstract}

>>>>

\begin{abstract}
% OLDER VERSION
%Sequential learning paradigms such as Continual Learning (CL) or Reinforcement Learning (RL) pose a challenge for gradient-based deep learning techniques as they struggle to incorporate new data and retain previous knowledge. Existing methods for converting neural networks from weight to function space allow a probabilistic treatment of the distribution over the function learned by the neural networks but are computationally expensive. We propose a method that converts a neural network to a low-rank functional representation as a sparse Gaussian process. With this approach, we can build a compact representation of the function encoded by the neural network that can replace previous data in continual settings and be used for fast adaptation in RL, avoiding full retraining of the model. 
%
% Rewrite on 2023-05-10
%Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and fail to retain previous knowledge. We present a method that mitigates these issues by transforming a weight-space neural network to a low-rank function-space representation, via the so-called dual parameters. In contrast to previous work, we model the joint distribution across the entire data set rather than a subset. This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance. We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining a compact representation in sequential learning.\looseness-1

Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting. We present a method that mitigates these issues by converting the neural network from weight-space to a low-rank function-space representation, via the so-called dual parameters. In contrast to previous work, we model the joint distribution across the entire data set rather than a subset. Our approach offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance. We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining an expressive functional representation for sequential learning.

\end{abstract}

%, maintaining a summary representation in continual learning,
